---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# simplebayes

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/kevgre/simplebayes/branch/main/graph/badge.svg)](https://app.codecov.io/gh/kevgre/simplebayes?branch=main)
<!-- badges: end -->

The goal of simplebayes is to allow the user to perform simple tasks in Bayesian statistics without requiring him or her to learn how to use a complex package such as Stan. This will allow the user to focus on the results of the model being built instead of how to build the model itself.

## Installation

You can install the development version of simplebayes from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("kevgre/simplebayes")
```

## Example

A common task in Bayesian statistics is to find the probability of a certain value in the posterior distribution given a binomial likelihood. The first step is to choose a prior. For a binomial likelihood, a common choice of prior is the beta distribution. With this, the posterior can be found as follows given some data:

```{r example}
library(simplebayes)
successes <- 20
sample_size <- 100

pbeta_post(0.3, successes, sample_size, likelihood = "binom")
```
